% ============================================================
%  references.tex — Bibliographie
%  Pour ajouter une reference : suivre le format \bibitem{key}
% ============================================================
\section*{Références}

\begin{thebibliography}{99}
  \bibitem{pycsp3}
    C.~Lecoutre, \textit{PyCSP3: Modeling Combinatorial Constrained Problems in Python},
    \url{https://pycsp3.org/}, 2020.

  \bibitem{ace}
    C.~Lecoutre, \textit{ACE: Adaptive Constraint Engine},
    CRIL, Université d'Artois,
    \url{https://github.com/xcsp3team/ACE}.

  \bibitem{xcsp3}
    F.~Boussemart, C.~Lecoutre, G.~Audemard, C.~Piette,
    \textit{XCSP3: An Integrated Format for Benchmarking Combinatorial Constrained Problems},
    \url{https://xcsp.org/}, 2016.

  \bibitem{networkx}
    A.~Hagberg, D.~Schult, P.~Swart,
    \textit{Exploring Network Structure, Dynamics, and Function using NetworkX},
    Proc. SciPy Conference, pp.~11--15, 2008.

  \bibitem{xtb}
    S.~Grimme, C.~Bannwarth, P.~Shushkov,
    \textit{A Robust and Accurate Tight-Binding Quantum Chemical Method for Structures,
    Vibrational Frequencies, and Noncovalent Interactions of Large Molecular Systems
    Parametrized for All spd-Block Elements (Z = 1--86)},
    J. Chem. Theory Comput., 13(5), pp.~1989--2009, 2017.

  \bibitem{gfn2xtb}
    C.~Bannwarth, S.~Ehlert, S.~Grimme,
    \textit{GFN2-xTB — An Accurate and Broadly Parametrized Self-Consistent Tight-Binding
    Quantum Chemical Method with Multipole Electrostatics and Density-Dependent Dispersion
    Contributions},
    J. Chem. Theory Comput., 15(3), pp.~1652--1671, 2019.

  \bibitem{benzai}
    Y.~Carissan, D.~Hagebaum-Reignier, N.~Prcovic, C.~Terrioux, A.~Varet,
    \textit{Benzai: a software for the generation of benzenoid systems},
    LS2N / LIS, 2021.

  \bibitem{varet2022}
    A.~Varet,
    \textit{Approches à base de contraintes pour la génération de structures benzenoïdes},
    Thèse de doctorat, Aix-Marseille Université, 2022.
\end{thebibliography}
